Stack Safety as a Security Property

### 2020-07-10 main.tex
One error in example-policy connection, one typo

Note that in this policy both the entry and exit sequences
must write to each element of
the frame, which can be quite expensive, especially for programs that
allocate large but sparsely populated frames; we return to this point
in \cref{sec:lazy}.
%
The running example in \cref{fig:running-trace-a} manages the stack in this way.
For example, {\tt f}'s ``blessed'' sequences allocate space to save its return
address (and private variables) in instructions 20--21, and later restores that
return address and deallocates its private frame space before returning in
34--36. Additionally, unlike in the simplified presentation of the policy, the
caller passes information to the callee through the stack, and for this creates
and initializes (23 and 24--25) and destructs (29) the argument part of the
callee's stack frame.\rb{The policy would also need to control this, I think it
  is clear}
%
%\rb{Note that we have also considered and implemented more flexible schemes
%  based on allowing operations above the current activation depth. How do we put
%  these together?}
%\rb{Do we want to discuss variations involving frame pointers or more implicit
%  return addresses, argument passing on the stack, alloc/dealloc, etc.?}
%\rb{Where to talk about the role of the compiler?}

@@

      Additional, for any variation \(\mach_0' \approx_{\mathit{Cof}(\mach_0),0}
      \mach_0\), taking the induced trace  \(\mach_0' \hookrightarrow
      \machT\), we must have \(\propdef{TraceConf} ~ \emptyset ~ \MPT ~ \machT\).

>>>>

Note that in this policy both the entry and exit sequences
must write to each element of
the frame, which can be quite expensive, especially for programs that
allocate large but sparsely populated frames; we return to this point
in \cref{sec:lazy}.
%
The running example in \cref{fig:running-trace-a} manages the stack in this way.
For example, {\tt f}'s ``blessed'' sequences allocate space to save its return
address (and private variables) in instructions 20--21, and later restores that
return address and deallocates its private frame space before returning in
34--36. Additionally, unlike in the simplified presentation of the policy, the
caller passes information to the callee through the stack, and for this creates
and initializes (22 and 24--25) and destructs (29) the argument part of the
callee's stack frame.\rb{The policy would also need to control this, I think it
  is clear}
%
%\rb{Note that we have also considered and implemented more flexible schemes
%  based on allowing operations above the current activation depth. How do we put
%  these together?}
%\rb{Do we want to discuss variations involving frame pointers or more implicit
%  return addresses, argument passing on the stack, alloc/dealloc, etc.?}
%\rb{Where to talk about the role of the compiler?}

@@

      Additionally, for any variation \(\mach_0' \approx_{\mathit{Cof}(\mach_0),0}
      \mach_0\), taking the induced trace  \(\mach_0' \hookrightarrow
      \machT\), we must have \(\propdef{TraceConf} ~ \emptyset ~ \MPT ~ \machT\).
